Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-12-02 paper/main.tex
added the tabulated version of thie Histogram of the number of gaps

    By applying the methodology described above to the whole set of simulations, we can reconstruct the history of close passages of Galactic globular clusters to Palomar~5's stream, in the last 5~Gyr, which -- we recall the reader -- is the time interval investigated in our simulations. The results of this analysis are reported in Fig.~\ref{fig:histogram_impact_time} and in Table~xx \paola{I suggest to report the results of Fig 3 also in a Table, in which we report for each GC which produced a gap, the time of close passage and the total number of gaps it generated.}. NGC~2808 impacts Palomar 5's stream about 200 Myr ago in 44 out of 50 simulations, creating a small gap at a similar position to the one reported in Fig.~\ref{fig:decomposition} in each case. Since this interaction occurred less than one orbital period ago, the uncertainties lead to orbital solutions remain that similar and thus producing consistent results across all simulations. However, as we continue to turn back time further, the uncertainties in the initial conditions allow the for the various orbital solutions to diverge from one another. Thus, in one configuration a cluster can impact the stream at a given time and yet at the same moment in a different set of initial conditions, it could be on the other side of the galaxy.

>>>>

    By applying the methodology described above to the whole set of simulations, we can reconstruct the history of close passages of Galactic globular clusters to Palomar~5's stream, in the last 5~Gyr, which -- we recall the reader -- is the time interval investigated in our simulations. The results of this analysis are reported in Fig.~\ref{fig:histogram_impact_time} and in Table~\ref{tab:gaps_per_perturber}. NGC~2808 impacts Palomar 5's stream about 200 Myr ago in 44 out of 50 simulations, creating a small gap at a similar position to the one reported in Fig.~\ref{fig:decomposition} in each case. Since this interaction occurred less than one orbital period ago, the uncertainties lead to orbital solutions remain that similar and thus producing consistent results across all simulations. However, as we continue to turn back time further, the uncertainties in the initial conditions allow the for the various orbital solutions to diverge from one another. Thus, in one configuration a cluster can impact the stream at a given time and yet at the same moment in a different set of initial conditions, it could be on the other side of the galaxy.

    \begin{table}[h]
      \centering
      \begin{tabular}{|ll|ll|ll|}
      \hline
      NGC2808 & 44 & NGC7089 & 5 & NGC5272 & 4 \\
      NGC6584 & 3 & NGC6341 & 2 & NGC6656 & 2 \\
      NGC104 & 2 & NGC3201 & 1 & NGC5634 & 1 \\
      NGC5286 & 1 & NGC362 & 1 & NGC5824 & 1 \\
      NGC6356 & 1 & NGC6333 & 1 & NGC6715 & 1 \\
      FSR1758 & 1 & NGC7078 & 1 & Pal10 & 1 \\
      \hline
      \end{tabular}
      \caption{The number of gaps created by each perturber across all 50 simulations of Palomar~5's tidal tail. This is the same data Fig.~\ref{fig:histogram_impact_time} but tabulated.}
      \label{tab:gaps_per_perturber}
      \end{table}
